### 2014-05-06 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: Add gas analyzer diagnostic information

>>>>

\chapter{Gas Analyzer}
\label{chap:Gas_Analyzer}

\section{Diagnostics}

The following screens provide useful diagnostic information that can be sent to technical support:

\begin{itemize}
\item To display the version and serial number, press Main $\rightarrow$ F5 $\rightarrow$ F10.
\item To display flow diagnostics, press Main $\rightarrow$ F3.
\item To display raw voltage/channel values, press Main $\rightarrow$ F5 $\rightarrow$ F6 $\rightarrow$ F2, then cycle through each gas using the left/right arrows.
\end{itemize}
